\documentclass[sigconf,screen]{acmart}

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, calc, decorations.pathreplacing}

% Colors for framework visualization
\definecolor{awarenessblue}{HTML}{3B82F6}
\definecolor{negotiationamber}{HTML}{F59E0B}
\definecolor{bnagreen}{HTML}{10B981}
\definecolor{gategray}{HTML}{6B7280}
\definecolor{constraintpurple}{HTML}{8B5CF6}
\definecolor{perceptionlight}{HTML}{DBEAFE}
\definecolor{comprehensionlight}{HTML}{BFDBFE}
\definecolor{projectionlight}{HTML}{93C5FD}
\definecolor{proposelight}{HTML}{FEF3C7}
\definecolor{deliberatelight}{HTML}{FDE68A}
\definecolor{resolvelight}{HTML}{FCD34D}
\definecolor{loopbg}{HTML}{F8FAFC}

\newcommand{\system}{\textsc{GroundingKit}}
\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
\newcommand{\dimicon}[1]{\tikz[baseline=-0.5ex]{\node[draw, rounded corners=2pt, fill=#1, minimum size=0.35cm] {};}}
\newcommand{\moment}[1]{\textsc{#1}}

\begin{document}

\title{Designing Coordination Infrastructure for Collaborative Writing}

\author{[Authors]}
\affiliation{\institution{[Institution]}}
\email{[email]}

\begin{abstract}
Collaborative writing requires teams to continuously negotiate shared understanding---what to write, how individual contributions relate to the collective goal, and when that goal should evolve. Yet current tools support only change-level awareness (track changes, real-time cursors, comments), leaving intent-level coordination unsupported. Teams can see \emph{what} each other wrote but cannot assess \emph{whether} that writing serves their shared plan or renegotiate the plan when it should change.

We address this gap in two steps. First, we define a \emph{coordination design space} for collaborative writing, organized around a boundary negotiating artifact (BNA) that externalizes team consensus. The BNA and writing form a \emph{negotiation space} connected by four types of relationships; a coordination pipeline---Awareness, Gate, Negotiation (Propose $\rightarrow$ Deliberate $\rightarrow$ Resolve)---operates on these relationships, with configurable dimensions at each stage. We derive this design space from a formative study with 3 teams (11 participants) and ground it in BNA theory, situational awareness, and conversation for action.

Second, we present \system{}, an open platform that operationalizes this design space. \system{} provides a foundation layer (abstract data model + view layer with entity-based UI slots), two declarative protocols (Awareness Protocol for sensing capabilities, Negotiation Protocol for coordination paths), and a guided team interface for configuring coordination pipelines. Developers contribute new capabilities through the same protocol used for built-in functions; teams configure their pipeline by answering questions about their collaboration context. We deploy \system{} with [N] teams and report findings on how teams define and use coordination infrastructure in practice.
\end{abstract}

\maketitle

\input{sections/introduction}
\input{sections/related-work}
\input{sections/formative-study}
\input{sections/framework-v7}
\input{sections/system-v2}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
